A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/paper.tex
Fix bibtex errrors.
Draft mode.

%     \author{}
    \author{
    Samuel R.\ Bowman$^{1,2,5,}$\thanks{The first two authors contributed equally.} \\
    \texttt{\small sbowman@stanford.edu} \\
    \And
    Jon Gauthier$^{2,3,5,*}$ \\
    \texttt{\small jgauthie@stanford.edu} \\
    \And
    Abhinav Rastogi$^{4,5}$ \\
    \texttt{\small arastogi@stanford.edu} \\
    \AND
    Raghav Gupta$^{6}$ \\
    \texttt{\small rgupta93@stanford.edu} \\
    \And
    Christopher D.\ Manning$^{1,2,5,6}$\\
    \texttt{\small manning@stanford.edu}\\
    \And
    Christopher Potts$^{1}$\\
    \texttt{\small cgpotts@stanford.edu}
    \AND\\[-3ex]
    {$^{1}$Stanford Linguistics\quad
    $^{2}$Stanford NLP Group\quad
    $^{3}$Stanford Symbolic Systems}\\
    {$^{4}$Stanford Electrical Engineering\quad
    $^{5}$Stanford AI Lab\quad
    $^{6}$Stanford Computer Science}
    }

@@

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\definecolor{black}{rgb}{0,0,0}
\makeatother
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}

>>>>

%     \author{}
    \author{
    Samuel R.\ Bowman$^{1,2,5,}$\thanks{~\,The first two authors contributed equally.} \\
    \texttt{\small sbowman@stanford.edu} \\
    \And
    Jon Gauthier$^{2,3,5,*}$ \\
    \texttt{\small jgauthie@stanford.edu} \\
    \And
    Abhinav Rastogi$^{4,5}$ \\
    \texttt{\small arastogi@stanford.edu} \\
    \AND
    Raghav Gupta$^{6}$ \\
    \texttt{\small rgupta93@stanford.edu} \\
    \And
    Christopher D.\ Manning$^{1,2,5,6}$\\
    \texttt{\small manning@stanford.edu}\\
    \And
    Christopher Potts$^{1}$\\
    \texttt{\small cgpotts@stanford.edu}
    \AND\\[-3ex]
    {$^{1}$Stanford Linguistics\quad
    $^{2}$Stanford NLP Group\quad
    $^{3}$Stanford Symbolic Systems}\\
    {$^{4}$Stanford Electrical Engineering\quad
    $^{5}$Stanford AI Lab\quad
    $^{6}$Stanford Computer Science}
    }

@@

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\definecolor{black}{rgb}{0,0,0}
\makeatother
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black, draft]{hyperref}
